%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Class
% Version 2.0 (12/10/23)
%
% This class originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Omar Roldan
% Based on a template by  Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}
\setlength{\columnsep}{0mm}
%----------------------------------------------------------------------------------------
\usepackage{lipsum}  


\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	{ \fontsize{16}{20} \textcolor{black}{\textbf{\MakeUppercase{El Zubeir Huweidi}}}}

	\vspace{6pt}

	{\Large Software Engineer}
\end{minipage}
\hfill
\begin{minipage}[t]{0.2\textwidth} % 20% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	\icon{Globe}{11}{\href{https://zizouhuweidi.github.io}{zizouhuweidi}}\\
	\icon{Phone}{11}{+218 91-6999968}\\
	\icon{MapMarker}{11}{Benghazi, Libya}\\

\end{minipage}
\begin{minipage}[t]{0.27\textwidth} % 27% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\icon{Envelope}{11}{\href{mailto:zubeir.huweidi@gmail.com}{zubeir.huweidi@gmail.com}}\\
	\icon{Github}{11}{\href{https://github.com/zizouhuweidi}{github.com/zizouhuweidi}}\\
	\icon{LinkedinSquare}{11}{\href{https://www.linkedin.com/in/el-zubeir-huweidi-900899234/}{/in/el-zubeir-huweidi-900899234}}\\

\end{minipage}


%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth}
	\cvsect{Summary}
	\vspace{-6pt}
	Backend Engineer interested in System Design and AI
	\vspace{-6pt}
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.465\textwidth}
	\cvsect{Skills}
	\vspace{-6pt}

	\begin{minipage}[t]{0.2\textwidth}
		\textbf{Languages:}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.73\textwidth}
		Go, Python, TypeScript, PHP, Java
	\end{minipage}
	\vspace{4mm}

	\begin{minipage}[t]{0.2\textwidth}
		\textbf{Technologies:}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.73\textwidth}
		Postgres, MySQL, Docker, Redis, gRPC, Kafka, RabbitMQ, Linux, Git
	\end{minipage}

\end{minipage}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Experience}
\begin{entrylist}
    \entry
    {6/2022 -- 9/2022}
    {Backend Engineer Intern}
    {UniQ Soft Technologies}
    {\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=-1pt]
            \item Worked on their accounting solutions and website.
        \end{itemize}
        \texttt{Java}, \texttt{Spring Boot}, \texttt{JavaScript}}
        
    \entry
    {7/2023 -- 9/2023}
    {Fullstack Engineer Intern}
    {AMA Group}
    {\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=-1pt]
            \item Responsible for collecting requirements, development, and deployment of the app.
            \item Developed a missions management dashboard.
        \end{itemize}
        \texttt{Go}, \texttt{Postgres}, \texttt{TypeScript}, \texttt{React}}
        
    \entry
    {1/2024 -- 7/2024}
    {Fullstack Engineer}
    {Prisma-Intl}
    {\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=-1pt]
            \item Capstone project: Redesigned a distributed network testing automation tool.
            \item Tested, fixed, and improved overall reliability.
            \item Identified bottlenecks and inefficiencies in the current architecture.
            \item Designed a new event-driven architecture that is both more resilient and extensible.
        \end{itemize}
        \texttt{Go}, \texttt{Postgres}, \texttt{gRPC}, \texttt{RabbitMQ}, \texttt{Docker}}
        
    \entry
    {12/2024 -- 3-2025}
    {AI Engineer}
    {EGate}
    {\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=-1pt]
            \item Developing a Retrieval-Augmented Generation (RAG) assistant.
            \item Responsible for data cleaning, processing, and setting up the Weaviate vector store.
            \item Exposed an internal FastAPI API to integrate the assistant.
            \item Optimizing the assistant's performance and experimenting with agent-like workflows.
        \end{itemize}
      \texttt{Python}, \texttt{OpenAI}, \texttt{Weaviate}, \texttt{LlamaIndex}, \texttt{FastAPI}, \texttt{Docker}}
        
    \entry
    {12/2024 -- Current}
    {Fullstack Engineer}
    {Libyan International Medical University}
    {\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=-1pt]
            \item Maintaining and improving internal platforms.
            \item Designing a better internal filesystem with AI-powered file search.
        \end{itemize}
        \texttt{PHP}, \texttt{Laravel}, \texttt{MySQL}, \texttt{Vue}}
    \entry
    {03/2024 -- Current}
    {Fullstack Engineer}
    {SadeemTech}
    {\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=-1pt]
            \item Maintaining and improving internal platforms.
            \item Designing a better internal filesystem with AI-powered file search.
        \end{itemize}
        \texttt{Go}, \texttt{Postgres}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------
\cvsect{Projects}
\begin{entrylist}
	\entry
	{Go, Python, React}
	{bayt-alhikmah}
	{https://github.com/ZizouHuweidi/bayt-alhikmah}
	{WIP knowledge management center}
	\entry
	{Typescript, React}
	{ractool}
	{https://github.com/ZizouHuweidi/ractool}
	{Club management tool for Rotaract club}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Education}
\begin{entrylist}
	\entry
	{9/2019 - 7/2024}
	{Software Engineering}
	{SMU Medtech}
	{Software Engineering degree at South Mediterranean School of Technology}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Languages}
\vspace{-6pt}

\hspace{26mm} \textbf{English} - Fluent, \textbf{ Arabic} - Native

%----------------------------------------------------------------------------------------

\end{document}
